Classical Planning with Simulators: \\ Results on the Atari Video Games

### 2015-02-10 ijcai15-paper/paper.tex
Removed space around item list
Hector changes

\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\frenchspacing
% \setlength{\pdfpagewidth}{8.5in}
% \setlength{\pdfpageheight}{11in}
\usepackage{enumitem}
%\setlist{nosep} % or \setlist{noitemsep} to leave space around whole list

@@

\author{\textbf{ID:} 320  \ \ ; \ \ \textbf{Keywords:} classical planning, search, video games}

@@

The action selection problem in the Atari games can be seen as a \emph{reinforcement learning} problem
\cite{sutton:book} over a deterministic MDP where the state transitions and rewards are not known, or alternatively,
as a  \emph{net-benefit planning problem} \cite{coles2012survey,keyder:jair09} with unknown state transitions  and  rewards. 
%\Omit{Namely} \Omit{While the \emph{reinforcement learning} problem seeks to synthesize a controller as a policy/function that maximizes 
%the reward of any trajectory\nir{NIR remark}}
While in the former a policy mapping every state $s$ to an action $a$ that maximizes expected reward is sought, in the latter one 
seeks an action sequence $a_0, a_1, \ldots, a_m$ from the  \emph{current}  state $s_0$ that generates
a state sequence $s_0, s_1, \ldots, s_{m+1}$ with  maximum  total reward $\sum_{i=0}^{m} r(a_i,s_i)$,
where $m$ is a sufficiently large planning horizon, and the rewards $r(a_i,s_i)$ and the  state-transitions $s_{i+1}=f(a_i,s_i)$
are known only after  action $a_i$ is applied in the state $s_i$.

@@

\begin{itemize}[noitemsep]
\item The \emph{novelty of a newly generate state $s$  in a  search algorithm}
is   $1$ if  $s$ is the first state generated in the search that makes true some  atom $X=x$,
else it is $2$ if  $s$ is the first state that makes a \emph{pair} of atoms $X=x$ and $Y=y$ true,
and so on.

\item  $\IW(i)$ is a breadth-first search that prunes newly generated states when their novelty \Omit{measure}
is greater than $i$.

\item $\IW$  calls $\IW(i)$ sequentially for $i=1,2,\ldots$ until a termination condition is reached,
returning then the best path found.
\end{itemize}

@@

\IW\ is a systematic and complete blind-search algorithm like breadth-first search (\BRFS) and iterative deepening (\ID),
but   unlike these algorithms, it uses the factored representation of the states in terms of variables to structure the
search. This structured exploration  has proved to be very effective over classical planning benchmark domains  when goals are  single atoms.\footnote{
Any conjunctive goal can be mapped into a single dummy atomic goal by adding an action that
achieves the dummy goal and that has the original conjunctive goal as a precondition.
Yet, this changes the definition of the domain.} For example, $37\%$ of the 37,921 problems
considered  in \cite{nir:ecai2012} are solved by $\IW(1)$ while $51.3\%$ are  solved by $\IW(2)$.
These are instances obtained from 37 benchmark domains by splitting problems with $N$ atomic
goals into $N$ problems with one atomic goal each.  Since $\IW(k)$ runs in time that is exponential in $k$, 
this mean that almost $90\%$ of the 37,921 instances are  solved in time that is either linear or quadratic in the number of problem variables, 
which in such encodings are all \emph{boolean}. Furthermore, when the performance of \IW\   is compared with  
a  Greedy Best First Search guided by the additive heuristic $h_{add}$, it turns out that ``blind'' \IW\ solves as many problems as the informed 
search, 34,627 vs. 34,849, far ahead of  other blind search  algorithms like \BRFS\ and \ID\  that solve 9,010 and 8,762 problems each. 
Moreover, \IW\ is  faster and results in shorter plans than in the heuristic search.

>>>>

\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\frenchspacing
% \setlength{\pdfpagewidth}{8.5in}
% \setlength{\pdfpageheight}{11in}

% \usepackage{enumitem}
% \setlist{nosep} % or \setlist{noitemsep} to leave space around whole list
% HG: better not play with spacing .. doesn't look as nice

@@

\author{\textbf{ID:} 320  \ \ ; \ \ \textbf{Keywords:} classical planning, search, video games, application}

@@

The action selection problem in the Atari games can be addressed  as a \emph{reinforcement learning} problem
\cite{sutton:book} over a deterministic MDP where the state transitions and rewards are not known, or alternatively,
as a  \emph{net-benefit planning problem} \cite{coles2012survey,keyder:jair09} with unknown state transitions  and  rewards. 
ALE supports the two settings: an \emph{on-line plannning setting} where  actions are selected
after a lookahead, and a \emph{learning setting}  that  must produce   controllers for mapping  states into
actions reactively without any lookahead. In this work we pursue the on-line planning approach where the lookahead
seeks  action sequences with  maximum  reward up to a certain horizon.

@@

\begin{itemize}
\item The \emph{novelty of a newly generate state $s$  in a  search algorithm}
is   $1$ if  $s$ is the first state generated in the search that makes true some  atom $X=x$,
else it is $2$ if  $s$ is the first state that makes a \emph{pair} of atoms $X=x$ and $Y=y$ true,
and so on.
\item  $\IW(i)$ is a breadth-first search that prunes newly generated states when their novelty \Omit{measure}
is greater than $i$.
\item $\IW$  calls $\IW(i)$ sequentially for $i=1,2,\ldots$ until a termination condition is reached,
returning then the best path found.
\end{itemize}

@@

\IW\ is a systematic and complete blind-search algorithm like breadth-first search (\BRFS) and iterative deepening (\ID),
but   unlike these algorithms, it uses the factored representation of the states in terms of variables to structure the
search. This structured exploration  has proved to be very effective over classical planning benchmark domains  when goals are  single atoms.\footnote{
Any conjunctive goal can be mapped into a single dummy atomic goal by adding an action that
achieves the dummy goal and that has the original conjunctive goal as a precondition.
Yet, this changes the definition of the domain.} For example, $37\%$ of the 37,921 problems
considered  in \cite{nir:ecai2012} are solved by $\IW(1)$ while $51.3\%$ are  solved by $\IW(2)$.
These are instances obtained from 37 benchmark domains by splitting problems with $N$ atomic
goals into $N$ problems with one atomic goal each.  Since $\IW(k)$ runs in time that is exponential in $k$, 
this means that almost $90\%$ of the 37,921 instances are  solved in time that is either linear or quadratic in the number of problem variables, 
which in such encodings are all \emph{boolean}. Furthermore, when the performance of \IW\   is compared with  
a  Greedy Best First Search guided by the additive heuristic $h_{add}$, it turns out that ``blind'' \IW\ solves as many problems as the informed 
search, 34,627 vs. 34,849, far ahead of  other blind search  algorithms like \BRFS\ and \ID\  that solve 9,010 and 8,762 problems each. 
Moreover, \IW\ is  faster and results in shorter plans than in the heuristic search.
